Since our project have two main goal:
\begin{itemize}
	\item compute the correlation between tweet and news
	\item create a summary of the main event that cause the sentiment shift
\end{itemize}
There are many work that are related with our. 
In particular, due to the incising and development of the Tweeter platform, in the last year a much work was done on the correlation and analysis of the tweeter data. Weiwei Guo et al.\cite{LTN} have propose a framework for link tweet with news and extract form the resulting correlation some missing aspect of the tweet-event. Instead of using a LSI technique for compute a text-to-word representation, they propose a methodologies based on the Weighted Textual Matrix Factorization\cite{WTMF} [WTMF] model. With the WTMF unsupervised model and the usage of cosine-similarity Weiwei Guo et al. were able to obtain good correlation performance and WTMF result to be a really strong tool for baseline create.

In the literature there is a lot of performed on the \emph{recommendation system}; some of this systems are developed for new recommendation: witch aims to recommend news articles based on a user features. This work seems to be complementary respect to our goal, but we focus on the correlation between tweet and news starting only with the tweet text content that is a much smaller and heterogeneous context respect to a user features. 

Recently Google present a system for sentence compression, in particular Google present a work for \emph{multi-sentence compression}\cite{MSC} focusing on the importance of content selection and the readable of the presentation.
Our attention was caught by the fact that Google obtain good result summary using only redundancy information without the usage syntactic constraints, so potentially can be used as an other language-independent methodology. Similarly to NGG the Google MSC approach use a graph representation of the text, combining it with some part of speech  information: obtaining a sentence compression.

